Psychophysics of musical elements in the discrete-time representation of sound

### 2013-10-04 article/article.tex
refeita parte de impulsos para ritmo, falta de fonte em movimento para frente

\subsubsection{Convolution for rhythm and meter}
It is possible to use a musical pulse -- such as specified by a BPM
tempo mark -- and to place an impulse at the start of each beat, with the purpose of
establishing metric and rhythms: the
convolution with an impulse shifts the sound to where
the impulse.
For example, two impulses equally spaced builds a binary division into the
pulse. Two signals, one with 2 impulses and another with 3 impulses, both 
equally spaced in the pulse duration, yields the pulse
maintenance with a rhythmic trace in which is easy to use binary or ternary
divisions of the pulse, as found in many ethnic or traditional music styles~\cite{Gramani}. 
Absolute values of the impulses implyes in proportions among the
amplitudes of the sonic incidences.
The use of convolution with impulses in this context is explored in the
music piece \emph{Trenzinho de caipiras impulsivos}. These features
embrace the creation of `sound amalgams' based on granular synthesis, for now refer specially to the
figure~\ref{fig:pulsoSubAgl}. This piece is a link to next section contents. 
The source code of the music piece is online, as part of the \massa toolbox.

\subsubsection{Moving audio source and receptor, Doppler effect}

Resuming the exposition in subsection~\ref{subsec:spac}: when an audio source
and a receptor are moving, their characteristics are ideally updated at each
sample of the digital signal. The speeds are decomposed in relation of each ear
direction. In this way, given the audio source speed (or velocity) $v_s$, that
is positive if the source moves away from receptor, and receptor speed $v_r$,
that is positive when it gets closer of the audio source, the frequency is given
by the well known Doppler effect:

>>>>

\subsubsection{Convolution for rhythm and meter}
It is possible to use a musical pulse -- such as specified by a BPM
tempo -- and to place an impulse at the start of each beat, with the purpose of
establishing metric and rhythms: the
convolution with an impulse shifts the sound 
to impulse position.
For example, two impulses equally spaced builds a binary division into the
pulse. Two signals, one with 2 impulses and the other with 3 impulses, both 
equally spaced in the pulse duration, yields a pulse
maintenance with a rhythmic in which eases both binary or ternary
divisions of the pulse, and this is found in many ethnic and traditional musical styles~\cite{Gramani}. 
Absolute values of the impulses implyes in proportions among the
amplitudes of the sonic reincidences.
The use of convolution with impulses in this context is explored in the
music piece \emph{Trenzinho de caipiras impulsivos}. These features
embrace the creation of `sound amalgams' based on granular synthesis, for now refer specially to the
figure~\ref{fig:pulsoSubAgl}. This piece is a link to next section contents. 
The source code of the music piece is online, as part of the \massa toolbox.

\subsubsection{Moving source and receptor, Doppler effect}

Summarizing the exposition in subsection~\ref{subsec:spac}: when an audio source
and a receptor are moving, their characteristics are ideally updated at each
sample of the digital signal. The speeds are decomposed in relation of each ear
direction. In this way, given the audio source speed (or velocity) $v_s$, that
is positive if the source moves away from receptor, and receptor speed $v_r$,
that is positive when it gets closer of the audio source, the frequency is given
by the well known Doppler effect:
